---
title: "Basic Trading Strategy"
output: html_notebook
---

Import Libraries
```{r}
library(quantmod)
library(TTR)
library(PerformanceAnalytics)
library(tidyverse)
```
Stores data as xts type objects - purpose built for handling time series data. They are matrices with an indexed time component.

```{r}
getSymbols("AAPL", src = "yahoo", from = "2020-01-01")
getSymbols("TSLA", src = "yahoo", from = "2020-01-01")
getSymbols("NFLX", src = "yahoo", from = "2020-01-01")
```
```{r charting-stock-prices}
barChart(AAPL, theme = chartTheme("black"))
barChart(TSLA, theme = chartTheme("black"))
barChart(NFLX, theme = chartTheme("black"))
```
# Technical Indicators


## 1.Simple Moving Average (SMA)

The standard interval of time we are using is 20 daysSMA and 50 days SMA. 

```{r SMA}
# AAPL
sma20_aapl <- TTR::SMA(AAPL$AAPL.Close, 20)
sma50_aapl <- TTR::SMA(AAPL$AAPL.Close, 50)

quantmod::lineChart(AAPL, theme = chartTheme("black"))
addSMA(n = 20, col = "blue")
addSMA(n = 50, col = "orange")
legend("left", col = c("green", "blue", "orange"),
       legend = c("AAPL", "SMA20", "SMA50"), lty = 1, bty = "n",
       text.col = "white", cex = 0.8)

# TSLA
sma20_tsla <- TTR::SMA(TSLA$TSLA.Close, 20)
sma50_tsla <- TTR::SMA(TSLA$TSLA.Close, 50)

quantmod::lineChart(TSLA, theme = chartTheme("black"))
addSMA(n = 20, col = "blue")
addSMA(n = 50, col = "orange")
legend("left", col = c("green", "blue", "orange"),
       legend = c("TSLA", "SMA20", "SMA50"), lty = 1, bty = "n",
       text.col = "white", cex = 0.8)

# NFLX
sma20_nflx <- TTR::SMA(NFLX$NFLX.Close, 20)
sma50_nflx <- TTR::SMA(NFLX$NFLX.Close, 50)

quantmod::lineChart(NFLX, theme = chartTheme("black"))
addSMA(n = 20, col = "blue")
addSMA(n = 50, col = "orange")
legend("left", col = c("green", "blue", "orange"),
       legend = c("NFLX", "SMA20", "SMA50"), lty = 1, bty = "n",
       text.col = "white", cex = 0.8)

```

## 2.Parabolic Stop and Reverse (SAR)

To calculate we pass on daily High and Low prices of companies along with a given acceleration value

```{r SAR}

sar_aapl <- TTR::SAR(cbind(quantmod::Hi(AAPL), quantmod::Lo(AAPL)), accel = c(0.02, 0.2))
barChart(AAPL, theme = "black")
addSAR(accel = c(0.02, 0.2), col = "lightblue")

sar_tsla <- TTR::SAR(cbind(quantmod::Hi(AAPL), quantmod::Lo(AAPL)), accel = c(0.02, 0.2))
barChart(AAPL, theme = "black")
addSAR(accel = c(0.02, 0.2), col = "lightblue")

sar_nflx <- TTR::SAR(cbind(quantmod::Hi(AAPL), quantmod::Lo(AAPL)), accel = c(0.02, 0.2))
barChart(AAPL, theme = "black")
addSAR(accel = c(0.02, 0.2), col = "lightblue")

```

## 3.Commodity Channel Index (CCI)

```{r CCI}

```

## 4.Rate of Change (ROC)

```{r ROC}

```

## 5.Stochastic Momentum Index (SMI)

```{r SMI}

```

## 6.Williams %R

```{r williamsR}

```

